Semantic Prediction in {R}ussian

### 2020-04-11 paper.tex
methodology-probabilities rework

Cloze task described in Taylor (1953) is an experiment in which one or more words are removed from a sentence and the participants are asked to fill in the missing content.

We used the dataset with cloze task answers from \cite{laurinavichyute}. The dataset is based on 144 sentences randomly selected from the Russian National Corpus (RNC, ruscorpora.ru) - an online corpus of Russian texts with extensive search options. These sentences were slightly edited: the authors replaced rare infrequent words with more frequent ones and shortened the sentences when they exceeded the preset maximum length of 13 words. The stimuli sentences were subjected to the cloze task experiment. Cloze task \cite{taylor:1953} is a test, commonly carried out for assessing native speakers of a language, which is aimed to understand respondents’ comprehension of a language and their ability to predict missing portions of written texts \cite{laurinavichyute}. This experiment presumes that native speakers can understand context and vocabulary to identify the correct semantic field or part of speech of a missing word.

In \cite{laurinavichyute}, the respondents were asked to successively predict the next words for each context. An example of stimuli that were shown to the participants is presented in Table 1 with corresponding correct next words and calculated predictability scores.

@@

For experiments, we used BERT trained on the Russian Wikipedia corpus
\cite{ruwiki}. To show differences between models, we will fine-tune BERT with our corpora.

>>>>

Cloze task described in \cite{taylor:1953} is an experiment in which one or more words are removed from a sentence and the participants are asked to fill in the missing content. It is commonly carried out for assessing native speakers of a language, which is aimed to understand respondents’ comprehension of a language and their ability to predict missing portions of written texts \cite{laurinavichyute}. This experiment presumes that native speakers can understand context and vocabulary to identify the correct semantic field or part of speech of a missing word.

We used the dataset with cloze task answers from \cite{laurinavichyute}. The dataset is based on 144 sentences randomly selected from the Russian National Corpus (RNC, ruscorpora.ru) - an online corpus of Russian texts with extensive search options. These sentences were slightly edited: the authors replaced rare infrequent words with more frequent ones and shortened the sentences when they exceeded the preset maximum length of 13 words. The stimuli sentences were subjected to the cloze task experiment. Respondents were asked to successively predict the next words for each context. An example of stimuli that were shown to the participants is presented in Table 1 with corresponding correct next words and calculated predictability scores.

@@

For experiments, we used BERT trained on the Russian Wikipedia corpus
\cite{ruwiki}. To show differences between models, we fine-tuned BERT with our corpora.
